A Formalization of Complete Discrete Valuation Rings and Local Fields

### 2023-12-12 HAL/CPP_paper_v2.tex
remove hyphen from type-class

\paragraph{Extensions and \code{valued} instances}
In \S\ref{subsec:extensions} we construct, for each field $K$ complete with respect to a discrete valuation~$v$ and every finite extension $L/K$, a unique valuation $v_L$ on $L$, recorded as \code{(v_L : valuation L}$\;\wzmZZ)$. However, at this level of generality we do not put a global \code{valued} instance on $L$: doing so would create infinitely many ``diamonds'', by which we mean the existence of two different procedures to endow an object with a certain mathematical structure (represented by two terms of the given structure that are propositionally, but not definitionally, equal). This leads to problems when exploiting the full force of the type-class inference mechanism: indeed, suppose that in a given context $\Gamma$, a term $t:T$ is well-typed assuming the existence of a term \code{s:S} for a certain structure \code{S}. Given two terms \code{s}$_1$,\code{s}$_2$\code{:S} that are propositionally equal, the corresponding terms \code{t}$_1$,\code{t}$_2$\code{:T} are different, yet carry the same mathematical information. Now, if the type-class inference mechanism can produce both terms \code{s}$_1$ and \code{s}$_2$ --- say, inside a proof --- the user would face the problem of having two different terms that look indistinguishable, which clearly leads to unexpected problems. In our setting, for every field $K$ that is complete with respect to a discrete valuation $v$, the original valuation is propositionally but not definitionally equal to its trivial extension $v_K$, resulting in two terms of the structure of a \code{valued} field on $K$: to avoid any diamond, we need to exclude the second from the inference search, and therefore we need to avoid declaring a structure of \code{valued} field on the trivial extension $K$ of $K$: this forces us to avoid declaring such a structure on \emph{every} extension $L/K$. Nevertheless, we provide a lemma \code{trivial_extension_eq_valuation}\href{https://github.com/mariainesdff/local_fields_journal/blob/0b408ff3af36e18f991f9d4cb87be3603cfc3fc3/src/discrete_valuation_ring/trivial_extension.lean#L63}{\extlink} proving the equality $v=v_K$.

>>>>

\paragraph{Extensions and \code{valued} instances}
In \S\ref{subsec:extensions} we construct, for each field $K$ complete with respect to a discrete valuation~$v$ and every finite extension $L/K$, a unique valuation $v_L$ on $L$, recorded as \code{(v_L : valuation L}$\;\wzmZZ)$. However, at this level of generality we do not put a global \code{valued} instance on $L$: doing so would create infinitely many ``diamonds'', by which we mean the existence of two different procedures to endow an object with a certain mathematical structure (represented by two terms of the given structure that are propositionally, but not definitionally, equal). This leads to problems when exploiting the full force of the typeclass inference mechanism: indeed, suppose that in a given context $\Gamma$, a term $t:T$ is well-typed assuming the existence of a term \code{s:S} for a certain structure \code{S}. Given two terms \code{s}$_1$,\code{s}$_2$\code{:S} that are propositionally equal, the corresponding terms \code{t}$_1$,\code{t}$_2$\code{:T} are different, yet carry the same mathematical information. Now, if the type-class inference mechanism can produce both terms \code{s}$_1$ and \code{s}$_2$ --- say, inside a proof --- the user would face the problem of having two different terms that look indistinguishable, which clearly leads to unexpected problems. In our setting, for every field $K$ that is complete with respect to a discrete valuation $v$, the original valuation is propositionally but not definitionally equal to its trivial extension $v_K$, resulting in two terms of the structure of a \code{valued} field on $K$: to avoid any diamond, we need to exclude the second from the inference search, and therefore we need to avoid declaring a structure of \code{valued} field on the trivial extension $K$ of $K$: this forces us to avoid declaring such a structure on \emph{every} extension $L/K$. Nevertheless, we provide a lemma \code{trivial_extension_eq_valuation}\href{https://github.com/mariainesdff/local_fields_journal/blob/0b408ff3af36e18f991f9d4cb87be3603cfc3fc3/src/discrete_valuation_ring/trivial_extension.lean#L63}{\extlink} proving the equality $v=v_K$.
